---
title: "Visualizing Time Series Data in R"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

## Contenido del curso

Este documento recopila las gráfica que se generan en el curso _Visualizing Time Series Data in R_ de DataCamp.
Como todos los cursos de DataCamp es de excelente calidad.

## Los datos
El primer archivo de datos contiene precios de acciones de cuatro importante compañías: Microsoft, Yahoo, Citigroup y Dow Chemical. En los gráficos a continuación se presentan las series de tiempo de los precios de las acciones.

```{r echo=FALSE, warning=FALSE}
library(dplyr)
library(xts)
library(zoo)
library(PerformanceAnalytics)
library(TTR)
```

```{r}
rm(list = ls())
data <- read.csv.zoo("dataset_1_1.csv", header = TRUE, sep = "", index.column=1, format="%Y-%m-%d")
data <- as.xts(data)
# Display the first few lines of the data
head(data, n=3)

# Display the column names of the data
tail(data, n=3)
```



```{r}
# Also reduce margin and character sizes by half
par(mfrow = c(4, 1), mex = 0.5, cex = 0.3)

# Replot yahoo data with labels for X and Y axes
plot(data$yahoo, main="Yahoo", type = "l", lwd = 2, las=1, xlab="date", ylab="price", col="dodgerblue4")

# Plot the second time series and change title
plot(data$microsoft, main="Microsoft", type = "l", lwd = 2, las=1, xlab="date", ylab="price", col="darkgreen")

# Plot the second time series and change title
plot(data$citigroup, main="Citigroup", type = "l", lwd = 2, las=1, xlab="date", ylab="price", col="darkorange")

# Plot the second time series and change title
plot(data$citigroup, main="Dow chemical", type = "l", lwd = 2, las=1, xlab="date", ylab="price", col="darkmagenta")
```



```{r}
# Change line color to red
plot(data$microsoft, type = "h", main="microsoft", sub="Daily closing price since 2015", las=1, xlab="date", ylab="price")
lines(data$microsoft, col = "green")
```



```{r}
# Replot with reduced margin and character sizes
par(mfrow = c(2, 1), mex = 0.6, cex = 0.8)
plot(data$yahoo, type = "l", las=1, main="yahoo")
plot(data$microsoft, type = "l", las=1, main="microsoft")
# x specifies location of legend in plot
legend(x = "bottomright",
         # legend specifies text label(s)
         legend = c("Stock X", "Stock Y"),
         # col specifies color(s)
         col = c("black", "red"),
         # lty specifies line type(s)
         lty = c(1, 1))
```

```{r}
# Plot the "microsoft" series
plot(data$microsoft, type = "l", las=1, main="Stock prices since 2015")

# Add the "dow_chemical" series in red
lines(data$dow_chemical, col = "red")

# Add a Y axis on the right side of the chart


# Add a legend in the bottom right corner
legend(x = "bottomright", legend = c("microsoft", "dow_chemical"),col = c("black", "red"), lty = c(1, 1)) 
```

```{r}
# Plot the "citigroup" time series
plot(data$citigroup, type = "l", las=1, main="Citigroup")

# Create vert_line to identify January 4th, 2016 in citigroup
vert_line <- which(index(data) == as.Date("2016-01-04"))

# Add a red vertical line using vert_line
abline(v = .index(data)[vert_line], col = "red")

# Create hori_line to identify average price of citigroup
hori_line <- mean(data$citigroup)

# Add a blue horizontal line using hori_line
abline(h = hori_line, col = "blue")
```

```{r}
# Create period to hold the 3 months of 2015
period <- c("2015-01/2015-03")

# Highlight the first three months of 2015 
chart.TimeSeries(data$citigroup, period.areas = period)
```
```{r}
# Highlight the first three months of 2015 in light grey
chart.TimeSeries(data$citigroup, period.areas = period, period.color="blue")
```

```{r}
# Plot the microsoft series
plot(data$microsoft, type = "l", las=1, main="Dividend date and amount", xlab = "date")
# Add the citigroup series
lines(data$citigroup, col = "orange", lwd=2) 


```

```{r}
# Same plot as the previous exercise
plot(data$microsoft, main = "Dividend date and amount", las=1, xlab = "date")
lines(data$citigroup, col = "orange", lwd = 2)


# Create the legend in the bottom right corner
legend(x = "bottomright", legend = c("micro", "citi"), col = c("black", "orange"), lty = c(1, 1))

```

```{r}
rm(list = ls())
data1 <- read.csv("dataset_2_1.csv", header = TRUE, sep = "")
names(data1)
data2<-read.zoo(data1, index.column = 1, format ="%Y-%m-%d")
data<-as.xts(data2)
colnames(data)<-"apple"
```

```{r}
#Plot Apple's stock price 
plot(data$apple, type = "l", las=1, main = "Apple stock price", xlab ="fecha")
```

```{r}
# Create a time series called rtn
rtn<-ROC(data$apple)

# Plot Apple daily price and daily returns 
par(mfrow = c(1, 2), mex = 0.6, cex = 0.5)

plot(data$apple, main = "Apple stock price")
plot(rtn, col = "forestgreen") 
```

```{r}
# Create a histogram of Apple stock returns
hist(rtn,
     breaks = 20,
     main = "Apple stock return distribution",
     xlab = "",
     probability=TRUE,
     col = "darkslategray1")
# Redraw a thicker, red density line
lines(density(rtn[-1,]), col="deeppink", lwd=2, lty=2)
```

```{r}
data(edhec)
class(edhec)
indice <- index(edhec)
```











